Short-term synaptic and neuronal plasticity act in synergy for deviance detection in spiking networks

### 2022-12-09 paper-1/manuscript.tex
Rev title

\title[Synaptic and somatic short-term plasticity collaborate to yield deviance detection]{Short-term synaptic plasticity and threshold adaptation act in synergy to give rise to deviance detection in a spiking model of neuronal culture}

>>>>

\title{Short-term synaptic and neuronal plasticity act in synergy for deviance detection in spiking networks}
